### 2018-03-01 Paper/jaccardbaetica.tex
add some bib

All the amphora stamps belong to Dressel 20 types. Dressel 20 was used to transport olive oil along the province during the Roman Empire. Most Dressel 20 were marked in stamps and tituli picti and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body.

>>>>

All the amphora stamps belong to Dressel 20 types \citep{martin-kilcher_romischen_1994}. Dressel 20 was used to transport olive oil along the province during the Roman Empire \citep{berni_millet_epigrafianforica_2008}. Most Dressel 20 were marked in stamps and tituli picti and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body.
